---
title: "DSC520Week9KalaivaniKalyan"
author: "Kalaivani Kalyanasundaram"
date: "8/8/2021"
output: word_document
---

# Week 9 Assignment

## Github link

https://github.com/kalaikalyan/hello-world

## Fit a binary logistic regression model to the data set that predicts whether or not the patient survived for one year (the Risk1Y variable) after the surgery. Use the glm() function to perform the logistic regression. See Generalized Linear Models for an example. Include a summary using the summary() function in your results.

```{r echo = FALSE}
library(foreign)
setwd("/Users/kalya/Documents/Kalai/dsc520")
surgery_df <- read.arff("data/ThoraricSurgery.arff")
log_model <- glm(surgery_df$Risk1Yr ~ surgery_df$DGN + surgery_df$PRE4 + surgery_df$PRE5 + surgery_df$PRE6 + surgery_df$PRE7 + surgery_df$PRE8 + surgery_df$PRE9 + surgery_df$PRE10 + surgery_df$PRE11 + surgery_df$PRE14 + surgery_df$PRE17 + surgery_df$PRE19 + surgery_df$PRE25 + surgery_df$PRE30 + surgery_df$PRE32 + surgery_df$AGE, surgery_df, family = binomial())
summary(log_model)
```
### According to the summary, which variables had the greatest effect on the survival rate?

Based on the summary, the variables that had the greatest effect are PRE9T , PRE14OC14, PRE17T, and PRE32T on the survival rate based on the p values.

### To compute the accuracy of your model, use the dataset to predict the outcome variable. The percent of correct predictions is the accuracy of your model. What is the accuracy of your model?

```{r echo = FALSE}
library(foreign)
library(caTools)
setwd("/Users/kalya/Documents/Kalai/dsc520")
surgery_df <- read.arff("data/ThoraricSurgery.arff")
split <- sample.split(surgery_df, SplitRatio = 0.8)
train <-subset(surgery_df, split == "TRUE")
test <- subset(surgery_df, split == "FALSE")
log_model <- glm(train$Risk1Yr ~ train$DGN + train$PRE4 + train$PRE5 + train$PRE6 + train$PRE7 + train$PRE8 + train$PRE9 + train$PRE10 + train$PRE11 + train$PRE14 + train$PRE17 + train$PRE19 + train$PRE25 + train$PRE30 + train$PRE32 + train$AGE, train, family = binomial())
res <- predict(log_model, test, type = "response")

res <- predict(log_model, train, type = "response")

confmatrix <- table(Actual_Value=train$Risk1Yr, Predicted_Value = res > 0.5)
confmatrix
accuracy <- (confmatrix[1,1] + confmatrix[2,2]) / sum(confmatrix)
accuracy
```

The accuracy is around 83%

## Fit a logistic regression model to the binary-classifier-data.csv dataset

### The dataset (found in binary-classifier-data.csv) contains three variables; label, x, and y. The label variable is either 0 or 1 and is the output we want to predict using the x and y variables.

```{r echo = FALSE}
library(foreign)
setwd("/Users/kalya/Documents/Kalai/dsc520")
binary_df <- read.csv("data/binary-classifier-data.csv")
log_model <- glm(binary_df$label ~ binary_df$x + binary_df$y , binary_df, family = binomial())
summary(log_model)
```

### What is the accuracy of the logistic regression classifier? Keep this assignment handy, as you will be comparing your results from this week to next week.

```{r echo = FALSE}
library(foreign)
library(caTools)
setwd("/Users/kalya/Documents/Kalai/dsc520")
binary_df <- read.csv("data/binary-classifier-data.csv")
split <- sample.split(binary_df, SplitRatio = 0.8)
train <-subset(binary_df, split == "TRUE")
test <- subset(binary_df, split == "FALSE")
log_model <- glm(binary_df$label ~ binary_df$x + binary_df$y , binary_df, family = binomial())
res <- predict(log_model, test, type = "response")
res <- predict(log_model, train, type = "response")

confmatrix <- table(Actual_Value=binary_df$label, Predicted_Value = res > 0.5)
confmatrix
accuracy <- (confmatrix[1,1] + confmatrix[2,2]) / sum(confmatrix)
accuracy
```
The accuracy is around 58.3% which is relatively lower.
